FraCaS: 80 percent complete

### 2019-03-01 paper2018/paper.tex
shorten
correct and clean
concluisions

\paragraph{Dynamic Monadic Semantics}
Dynamic Monadic Semantics have been proven to be an effective way of
dealing with anaphora and ellipsis. There are a number of approaches
using monads or other equivalent constructions (e.g. continuations as in the work of
\citet{de2006}) for anaphora and ellipsis
\citet{Shan:2002,unger:2011,Barker:04,de2016,charlow:2017}. In this
paper, we follow the approach described in
\citet{bernardy_jolli}. More details on this will be given in the next
section.

@@

\paragraph{definites} A naive way to handle definites is an
existential (or sigma). However, if the semantics does not feature a
dynamic element, then the existential quantification is introduced
locally. This means that the quantifier can be introduced in the wrong
context. Consider the phrase ``everyone pets the dog''. The structure
of the interpretation would be
$∀x. person(x) → ∃y. dog(y) ∧ pet(x,y)$.

Instead, our take is that definites should be treated as an anaphoric
expression with an implicit referrent. That is, if the referent is not
found in the discourse, then it will be forcibly introduced, using an
existential type, \emph{at the top-level} of the expression. To be
able to do this, we record all definites without referent, using
another portion of the environment (using a monadic effect).
%SC
%For the
%above example, we obtain the desired interpretation:
%$∃y. dog(y) ∧ (∀x. person(x) → pet(x,y))$.

@@

\paragraph{Adjectives}
In our system, we interpret gradable adjectives using a pair of a
measure $m : objects → Z$ and a threshold $τ : Z$, where $Z$ is
treated as an abstract ordered ring by Coq. (This structure has no
dynamic aspect in our model, and thus is entirely handled within Coq.)
For subsective adjectives, $τ$ will additionally depend on the class
of the object in question. This structure has the benefit that
opposite adjectives can be easily represented (measures are opposites
$∀x. m_1 x = -m_2 x$ and thresholds do not overlap $τ_1 + τ_2 >
0$). Formalization aside, this idea is reminiscent of degree-based
approaches to gradable adjectives of
\citet{Cresswell:1976,Kennedy:2007}.  Additionally
adjectival predicates, as present in the FraCaS suite, are interpreted as
linear inequations in $Z$. Solving systems of such inequations is
decidable.
% SC
%Indeed, the tactic that Coq offers for this purpose can
%solve all such problems in the FraCaS suite, automatically.

@@

\section{Conclusions and Future Work}

>>>>

\paragraph{Dynamic Monadic Semantics}
Dynamic Monadic Semantics have been proven to be an effective way of
dealing with anaphora and ellipsis. There are a number of approaches
using monads or other equivalent constructions (e.g. continuations as in the work of
\citet{de2006}) for anaphora and ellipsis
\citet{Shan:2002,unger:2011,Barker:04,de2016,charlow:2017}. In this
paper, we follow the approach described in
\citet{bernardy_jolli}. More details are given in the next
section.

@@

\paragraph{definites} A naive way to handle definites is using an
existential type. However, if the semantics does not feature a
dynamic element, then the existential quantification is introduced
locally. This means that the quantifier can be introduced in the wrong
context. Consider the phrase ``everyone pets the dog''. The structure
of the interpretation would be
$∀x. person(x) → ∃y. dog(y) ∧ pet(x,y)$.
%
Instead, our take is that definites should be treated as an anaphoric
expression with an implicit referrent. That is, if the referent is not
found in the discourse, then it will be forcibly introduced, using an
existential type, \emph{at the top-level} of the expression. To be
able to do this, we record all definites without referent, using
another portion of the environment (using a monadic effect).
%SC
%For the
%above example, we obtain the desired interpretation:
%$∃y. dog(y) ∧ (∀x. person(x) → pet(x,y))$.

@@

\paragraph{Adjectives}
We interpret gradable adjectives using a pair of a
measure $m : objects → Z$ and a threshold $τ : Z$, where $Z$ is
treated as an abstract ordered ring by Coq. (This structure has no
dynamic aspect in our model, and thus is entirely handled within Coq.)
For subsective adjectives, $τ$ will additionally depend on the class
of the object in question. This structure has the benefit that
opposite adjectives can be easily represented (measures are opposites
$∀x. m_1 x = -m_2 x$ and thresholds do not overlap $τ_1 + τ_2 >
0$). Formalization aside, this idea is reminiscent of degree-based
approaches to gradable adjectives of
\citet{Cresswell:1976,Kennedy:2007}.  Additionally
adjectival predicates, as present in the FraCaS suite, are interpreted as
linear inequations in $Z$. Solving systems of such inequations is
decidable.
% SC
%Indeed, the tactic that Coq offers for this purpose can
%solve all such problems in the FraCaS suite, automatically.

@@

\section{Conclusions and Future Work}
We presented a system using  GF, Dynamic Semantics and Coq, essentially converting GF trees to Coq types using dynamic semantics. The system outperforms the state of the art in logical approaches when tested on the FraCaS test suite and is the only system to date that has performed a run on the ellipsis/anaphora section of the FraCaS. The system's precision  can form the start of a very precise NL reasoner for controlled domains. For the future, we plan to  extend the system to cover the remaining section of the FraCaS (tense/aspect), and also develop a more applied version to perform reasoning on controlled NL domains.
